Holomorphic field theories and higher algebra

### 2022-12-02 draft.tex
weak version

\subsection{A relation to Hori-Tong duality}

A duality

The basic two-dimensional supersymmetric theories involved in both sides of this duality are particular gauged linear $\sigma$-models (GLSMs) with $\cN=(2,2)$ supersymmetry. 
The physics terminology for the supersymmetric GLSM is a two-dimensional $\cN=(2,2)$ supersymmetric gauge theory coupled to some number of chiral multiplets transforming in a particular representation.
For gauge group $U(N)$, one takes $F_f$ chiral multiplets valued in the fundamental representation $\CC^N$ and $F_a$ chiral multiplets valued in the anti-fundamental representation.

@@

\begin{lem}
For a holomorphic QCD theory, this compactification is a Landau-Ginzburg B-model for \owen{finish! would it be easier just to spell out what happens to matter, gauge, and the QCD?}
\end{lem}

@@

\begin{conj}
\owen{Unpack in some detail.}
\end{conj}

This conjecture is essentially due to Hori and Tong. \owen{Add some history, cite some references.}

>>>>

\subsection{Two-dimensional TFTs by compactification}

@@

\begin{lem}
For a holomorphic QCD theory $\cT(F,N)$, this compactification is a Landau-Ginzburg B-model~$\cT(F,N)_2$.
\owen{Not sure what's the best way to characterize which one we get.}
\end{lem}

@@

\begin{conj}
There is an equivalence between $\cT_{\sfE}(F,N)_2$ and $\cT_{\sfM}(F,N)_2$, 
the compactifications of the electric and magnetic holomorphic QCD theories.
\end{conj}

This conjectured equivalence resembles Hori-Tong dualities \cite{HoriTong, Hori, others}.
(In those papers, it is often said that Hori-Tong dualities are like Seiberg dualities!)
We hope that insights from the study of these dualities --- such as the deep work on homological projective duality \cite{Kuznetsov, Thomas, Segal, others} ---- might apply here, and also feed back towards holomorphic Seiberg duality.

%A duality 
%
%The basic two-dimensional supersymmetric theories involved in both sides of this duality are particular gauged linear $\sigma$-models (GLSMs) with $\cN=(2,2)$ supersymmetry. 
%The physics terminology for the supersymmetric GLSM is a two-dimensional $\cN=(2,2)$ supersymmetric gauge theory coupled to some number of chiral multiplets transforming in a particular representation.
%For gauge group $U(N)$, one takes $F_f$ chiral multiplets valued in the fundamental representation $\CC^N$ and $F_a$ chiral multiplets valued in the anti-fundamental representation.
